Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-08-16 ehp_revision/response_to_reviewers.Rmd

- Future research could expand the work by [@grabich2015measuring] to determine
the extent of these issues with use of FEMA disaster declarations for
epidemiological exposure assessment. This would need to go beyond the comparison
with exposure assessment based on storm hazards, because sometimes the
characteristics of the affected community modifies the amount of disaster that
results from hazards of a certain severity. For example, a community that it
exposed often might be more "hardened" against damage from the storm (any work
from Seth on this) and so might experience less infrastructure damage from a
tropical cyclone with certain characteristics compared to a community that is
rarely exposed to tropical cyclones. One interesting direction would be to
investigate if there is evidence of differences in probablity of disaster
declarations at geopolitical boundaries, like when comparing counties on either
side of a state border.

There are some cases where damage reports are directly used to infer the
intensity of the weather event. For example, damage surveying is used following
a tornado to assign the tornado's class on the [enhanced] Fujita scale. However,
this is not the intent of FEMA damage reports, which instead are used to
determine post-disaster aid [?] and are influenced by a number of political
factors.

> "Because of the historic lack of direct measurements and remotely sensed
tornado wind speeds at or near group level, damage surveying has remained the
most common form for indicating tornado strength. ... The occurrence of a direct
tornado strict upon a fixed, sufficiently sturdy, and well-calibrated wind
measuring station is quite rare. Only 31 direct in situ tornado observations are
evident between 1894 and 2011." [@edwards2013tornado]

This question could be explored to some degree through a study that uses the 
physical hazard data provided in this dataset as the exposure and FEMA disaster
declarations as the outcome. Such a study could clarify the degree to which 
each hazard---and its intensity---helps in explaining that probablity that 
a disaster declaration is issued. It could also clarify the degree to which 
other factors, beyond the intensity of these hazards, drive the probability of
a county receiving a disaster declaration. For example, if two counties 
are exposed to a storm-associated hazard of the same intensity, they may 
still have different probabilities of associated societal impacts, as a 
community that is regularly exposed to that hazard may be more "hardened" 
against it. Other differences in infrastructure and factors associated with 
vulnerability could similarly introduce variability.

At a more complex level, studies could explore the causal pathways from the 
initial physical hazard to resulting damage/property loss through to associations
with health outcomes, to provide a clearer idea of the direct and indirect 
pathways leading to health impacts from tropical cyclones.

For both of these studies, however, there may be better sources of damage
estimates to use than FEMA disaster declarations. FEMA disaster declarations 
can be prone to political and other influences, and since their primary function
is not to record damage but rather to be a step in getting help to communities, 
they can be problematic to use as an unbiased estimate of damage levels in 
epidmiological research. One study, for example, found ... . There are other
estimates of property damage that might be less problematic, including the 
estimates recorded in NOAA's Storm Events database and data from private 
insurers, although the quality of disaster loss data is well known to be
less than ideal for secondary research [can be prone to bias through a number
of mechanisms] [ref to Gall paper?].

### 2020-08-17 ehp_revision/response_to_reviewers.Rmd

This question could be explored to some degree through a study that uses the 
physical hazard data provided in this dataset as the exposure and FEMA disaster
declarations as the outcome. Such a study could clarify the degree to which 
each hazard---and its intensity---helps in explaining that probablity that 
a disaster declaration is issued. It could also clarify the degree to which 
other factors, beyond the intensity of these hazards, drive the probability of
a county receiving a disaster declaration. For example, if two counties 
are exposed to a storm-associated hazard of the same intensity, they may 
still have different probabilities of associated societal impacts, as a 
community that is regularly exposed to that hazard may be more "hardened" 
against it. Other differences in infrastructure and factors associated with 
vulnerability could similarly introduce variability.

At a more complex level, studies could explore the causal pathways from the 
initial physical hazard to resulting damage/property loss through to associations
with health outcomes, to provide a clearer idea of the direct and indirect 
pathways leading to health impacts from tropical cyclones.

For both of these studies, however, there may be better sources of damage
estimates to use than FEMA disaster declarations. FEMA disaster declarations 
can be prone to political and other influences, and since their primary function
is not to record damage but rather to be a step in getting help to communities, 
they can be problematic to use as an unbiased estimate of damage levels in 
epidmiological research. One study, for example, found ... . There are other
estimates of property damage that might be less problematic, including the 
estimates recorded in NOAA's Storm Events database and data from private 
insurers, although the quality of disaster loss data is well known to be
less than ideal for secondary research [can be prone to bias through a number
of mechanisms] [ref to Gall paper?].

FEMA declaration is largely subjective, requiring state governors and/or tribal
chiefs to submit a proposal for government aid on the basis that local resources
are overwhelmed [@FEMA]. As a result, using FEMA disaster declarations as
exposure classification to hurricanes restricts exposure to 1) those states
whose resources are overwhelmed and 2) those states who apply for FEMA aid.
(FEMA is likely less objective given societal effects (politics) [@Kunkel1999])
As a result, other severely impacted counties and states that may not fit FEMA
criteria are excluded and may therefore be incorrectly identified as unexposed,
preventing researchers from assessing the full impact of a given hurricane
[JMF-- the Grabich 2016 study actually found that FEMA assigned the highest
exposure, and may overestimate the health effects of a hurricane; GBA-- let's
think about why that might have had "false positives". I think that would be an
interesting point to include here.]. Researchers have found heterogeneity in
exposure assignments of counties, both within and between storms, when different
metrics of exposure are used [@Grabich2016; @Grabich2015]. Such
missclassification can have important consequences in assessments of the public
health and economic impacts of tropical storms.

One study used FEMA disaster declarations as a binary indicator of tropical
storm exposure [@Grabich2016]. They found that this metric tended to assess a
lot more counties as "exposed" to a storm than distance- or wind-based metrics
[@Grabich2016], although they only compared the two exposure metrics as applied
to four storms (Hurricanes Charley, Frances, Ivan, and Jeanne in Florida in
2004).

Data on storm impacts, including property damage or insurance claims data, are
sometimes available through storm databases or publications (e.g., NOAA's Storm
Events data, *Monthly Weather Review*). While such data could potentially be
used to create an exposure metric, tropical storm damage data requires some
normalization, to incorporate both changes in dollar value over time and also
changes in development in at-risk areas, to be comparable over extended time
periods [@Pielke1998].

@@

We have moved other suggestions that you sent in "Track Changes" of the Word 
document for the original manuscript and address each in detail below.

The largest-scale county-level exposure study is likely that of @Zandbergen2009,
which estimated exposure in US counties to all US landfalling Atlantic basin
tropical storms between 1851 and 2003, using both distance and an exposure
metric that incorporated distance and windspeed. They used this exposure
evaluation to create maps of total exposure to tropical storms within US
counties, as well as to explore associations between a county's long-term
exposure to tropical storms and its location, distance from the coast, size, and
shape [@Zandbergen2009]. @Kruk2010 explored exposure to hurricane-related winds
in the United States, including inland areas, for 1900-2008.

Geographical patterns can differ for these different
storm hazards, and so exposure assessment based on one hazard could create
exposure misclassification if the pathway for health risks is through a
different storm hazard.

A tropical cyclone's high winds can bring health risks and property damage
through structural damage of houses and other buildings, falling trees, and
wind-borne debris [@rappaport2000] and cause power
outages [@liu2005; han2009], which introduce a number of threats to
human and ecological health, including water quality risks if the outage affects
wastewater treatment plants [@mallin2006].  Other risks can exist
without severe wind; for example, one study found that most of the direct
hurricane-related deaths in the US between 1970 and 1999 occurred in cases
when wind was below hurricane strength, including for Tropical Storms Charley
in 1998 and Alberto in 1994 [@rappaport2000].  Tropical cyclones can
produce excessive rain, especially in certain topographies (e.g., near
mountains), so counties well inland sometimes experience more extreme rain than
coastal counties. Flood risks from tropical cyclones can result from this rain,
although the two risks are not perfectly correlated [@chen2015]. In the
US, over half of hurricane-related direct deaths from 1970 to 1999 from
Atlantic basin storms were a result of freshwater
flooding [@rappaport2000]. Flooding can also degrade water
quality [@mallin2006], which can threaten both human and ecological
health.

If a study misclassifies exposure to the hazard or hazards that cause the
health risk being studied, the study will generate biased estimates of tropical
cyclone risks and impacts. Further, when different studies use different
methods to assess exposure to tropical cyclones, their results are difficult to
meaningfully compare and aggregate. If different methods identify
similar sets of communities as ``exposed'',  these concerns are less serious.
However, if different methods differ substantially in which communities they
identify as ``exposed'', it makes it very important that epidemiological
studies are thoughtful in how they assess exposure.

These analyses can also help researchers compare and interpret results from
previous epidemiological studies that have assessed tropical cyclone exposure in
different ways, helping to [synthesize] previous epidemiologic results to form a
better picture of how these storms can affect human health.

However, these frequency maps, together with evidence from
specific tropical cyclones (Figures \ref{fig:ivanexposure}
and \ref{fig:jaccard}),  do illustrate the potential for strong differences in
spatial patterns in tropical cyclone exposures, depending on which tropical
cyclone hazards are considered.  A few previous studies have sought to
determine county-level exposure to tropical cyclones over multi-year periods,
including @zandbergen2009, which estimated exposure in US
counties to all US landfalling Atlantic-basin tropical cyclones
between 1851 and 2003, using both a distance-based metric and a metric that
combined distance and windspeed, and [@kruk2010], which explored
exposure to hurricane-related winds in the US, including inland areas,
for 1900--2008.  Our results suggest that such exposure assessments may
perform well in capturing some tropical cyclone hazards (e.g., wind), but
likely miss other potentially dangerous tropical cyclone exposures, especially
for hazards that repeatedly threaten northern or inland counties (e.g., rain,
flooding).

Therefore, use of distance to assess tropical cyclone exposure for impact
studies could result in problematic exposure misclassification, which could mask
true associations, even strong associations, between tropical cyclone exposure
and outcomes of interest in impact studies [@savitz2016interpreting;
armstrong1998effect]. The use of a single hazard-based metric (e.g., wind) could
cause similar problems if the impact is driven, at least in part, by a different
hazard or by multiple hazards of the tropical cyclone.

If measurements of one storm hazard are used as a proxy to capture exposure to
a different hazard, or a non-hazard proxy like distance to the storm track is
used to assess exposure to storm hazards, the resulting exposure
misclassification could be differential (i.e., associated with the outcome of
interest or with factors associated with risk of the outcome of interest).

Therefore for most tropical cyclones, since exposure assessments often differ
across storm hazards, as well as between each storm hazard and a distance-based
proxy measurement, exposure misclassification is a potential risk.

Further, we investigated agreement in exposure assessment across these metrics
when applied individually. We found large differences in which counties are
exposed to different hazards of tropical cyclones and that distance is, at
best, a moderate, and often a very poor, surrogate for exposure to the specific
tropical cyclone hazards of high wind, extreme rainfall, flooding, and
tornadoes. Use of distance as a surrogate for any of these hazards, or exposure
assessment based on one hazard when the pathway for health impacts is in part
or full through another storm hazard, could lead to exposure misclassification.
In the case of tropical cyclone risk and impact studies, including
epidemiological studies, this would result in biased estimates.  Our findings
highlight the importance of clarifying the potential pathway from tropical
cyclone hazards to health impacts when conducting tropical cyclone
epidemiological studies, and then basing exposure assessment on these hazards.

@@

\textit{Lines 276--281 from original manuscript:}

\begin{quotation}
\noindent
\textit{"To identify flood- and tornado-based tropical cyclone exposures in US
counties, we matched storm tracks with event listings from the National Oceanic
and Atmospheric Administration (NOAA)’s Storm Event Database (NOAA NCEI 2020).
While this database has recorded storm data, particularly tornadoes, since 1950,
its coverage changed substantially in 1996 to cover more types of storm events,
including flood events (NOAA NCEI 2020). We therefore only considered flood
metrics of tropical cyclone exposure for storms in 1996 and later."}
\end{quotation}
\end{shaded}

**Response:**

As suggested, we have added that these events are based on reports in the
Methods, in addition to our previous discussion of the point in the Discussion:

> **Revised text (relevant addition in bold):**
To identify flood- and tornado-based tropical cyclone exposures in US counties,
we matched storm tracks with event listings from the National Oceanic and
Atmospheric Administration (NOAA)’s Storm Event Database (NOAA NCEI 2020).
**Events are listed in this database based on reports from ... and other
sources.** While this database has recorded storm data, particularly tornadoes,
since 1950, its coverage changed substantially in 1996 to cover more types of
storm events, including flood events (NOAA NCEI 2020). We therefore only
considered flood metrics of tropical cyclone exposure for storms in 1996 and
later."

@@

\textit{Lines 294--295 from original manuscript:}

\begin{quotation}
\noindent
\textit{"The tornado observations from this dataset form a traditional tornado
event database for the US, and so we did not further validate the tornado event
data."}
\end{quotation}
\end{shaded}

**Response:**

This database is NOAA's database of records on tornado events in the United 
States. It is the original source for the only other national tornado database
available for the country (the SPC's ...), which provides a version of the 
same data in which tornado events are joined into a single record in cases where 
they cross county lines. There is no other comparable source of data on tornado
occurrences that could be used for a comparison as validation.

@@

> "During the early 1950s, the US Weather Bureau began a concerted effort to
count all US tornadoes. In 1950, a list of tornadoes was provided in the
*Climatological Data National Summary*, but it was not until 1953, the first
full year of the issuance of Weather Bureau tornado watches, that the agency
began to formally count all tornadoes. The *Climaticalogical Data National
Summary* document evolved into *Storm Data* by 1959, which, in addition to
tornado data, included information on other storm perils, such as severe hail,
high winds, and floods (Grazulis 1993). Over the years, the tornado dataset has
been formatted and adjusted by the National Severe Storms Forecast Center and
Storm Prediction Center (SPC), and currently the National Tornado Database is
administered by the NWS Headquarters, SPC, and NCDC (McCarthy 2003)."
[@Ashley2007]

\begin{shaded}
\textbf{R3 Comment 6:}
Table 1: I suggest providing the rationale for picking the thresholds for
classifying continuous exposures into binary ones within the table. 
\end{shaded}

**Response:**

For all outcomes, there are various reasonable choices that can be picked for
the threshold in defining exposure. There is not room to go into these details
within Table 1, so instead we added a separate table to the Supplemental
Material that provides both some reasoning behind the thresholds selected in
this study and also other reasonable thresholds that could be considered.
Ultimately, this choice will depend on what a researcher considers as plausible
causal pathways for the outcome he or she is studying. For example, if power
outages form a plausible step in the pathway, then the threshold for gale-force
or strong gale-force winds might be reasonable, while if the pathway is more
likely to be through larger-scale building destruction, a higher threshold would
be more reasonable. Some studies have done sensitivity analyses to consider how
results changed using different exposure metrics. For example, @Czajkowski2011
performed a sensitivity analysis using different assumptions about wind decay
away from the center of a storm, while @Currie2013, who used a distance-based
exposure metric, considered different buffer distances as a sensitivity
analysis.

- **Wind:** This threshold is the threshold for gale-force and higher winds
based on the Beaufort wind scale. This value is used by the National Hurricane
Center [?] as the outer limit of winds for its wind radii product in storm 
tracking data. Other reasonable choices for a threshold of wind exposure 
could include the two more intense thresholds also used in the NHC [?] wind
radii estimates of storm extent (50 knots and 64 knots, the later of which 
is the threshold for hurricane-force winds on the Beaufort Scale) or other
thresholds on the Beaufort Scale (e.g., "strong gale", which starts at 
41 knots; "storm", which starts at 48 knots; "violent storm", which starts
at 56 knots).

- **Rain:** This threshold is ... Other reasonable thresholds might be ... or
might incorporate different ranges of days around the storm's closest approach
to a county in calculating the cumulative precipitation. For example, ... For
the most part, using our window (two days before to one day after a storm's
closest approach) captured most of the storm-associated precipitation that would
have been counted using a wider window from five days before to two days after a
storm's closest approach, even for a large, slow storm. However, for a storm
that loops and so passes some counties twice, such as Allison (2001), this
four-day window may not be adequate, and lead to an underestimation of total
rainfall associated with the storm relative to estimates for faster-moving
storms. Other storms that looped over or near land and so passed close to US
counties twice include Allison (1989), Alberto (1994), Gordon (1994), Dennis
(1999), Edouard (2002), Fay (2002), Alex (2004), Ivan (2004), Dennis (2005), and
Ophelia (2005). One difficulty in measuring rain exposure consistently across
many different storms is how many days to include in the rain total. Some
storms, especially ones associated with dangerous rainfalls, can move very
slowly, meaning a window of several days needs to be used to fully capture
storm-related rainfall. For example, one study used a period of over four days
to provide storm rainfall totals from the slow-moving Hurricane Danny in 1997
[@Medlin2007]. Single-storm studies often measure rainfall as the total rainfall
over the full "event" (e.g., Medlin2007); however, the timing of the event is
determine in a customized way for each storm, making it difficult to extend to
multi-storm analyses. We included more days prior to the storm because
storm-related rains often precede the passing of the storm's center [ref].

- **Distance:** This threshold is one that has been commonly used in studies in
which distance from the storm's track is used as a proxy for tropical cyclone
exposure (for example, [refs]). Further, [anything in relation to storm size?].
Other reasonable thresholds for distance include ..., all of which have also
been used in previous research in assessing tropical cyclone exposure using
distance from the storm's track as a proxy. Other distance-based exposure
metrics have defined "exposure" to occur only when a storm's center track passes
through a county's boundary (e.g., @Zandbergen2009, who describe this metric of
exposure as a "hit" on the county; @Kinney2008 is another example that
considered highest exposures for counties directly on the storm's path). This
way of measuring exposure can exclude nearby counties that suffered extreme
conditions from the storm but were not directly on the hurricane's track
[@Kruk2010], especially since hurricanes can have a width ([typical storm width;
citation])[JMF-- Weatherford and Gray paper referenced in Grabich 2016 may be a
good place to start. Suggest 30-60km width of the eye of the storm itself] that
is much larger than a typical county's width and since a hurricane's maximum
winds can extend well away from the storm's center. Further, exposure assessed
using this method is associated with the size [@Zandbergen2009; @Kruk2010] and
shape [@Zandbergen2009] of a county. (While some studies have avoided this
problem by determining exposure for equal-area grid cells (e.g., [@Kruk2010]),
in studies where exposure needs to be matched with a county-level outcome, some
process of aggregation from grid cells to counties would still need to be
performed.) By contrast, assessing distance-based exposure based on measuring
distance between the storm track and each county's center would be less
susceptible to differences in county size and shape and so might be a more
reliable metric of exposure than determining if a storm track ever crossed a
county boundary. Further, assessing the minimum distance between county center
and the storm track, as we do here, allows for a continuous, rather than binary,
metric of distance-based exposure to a storm. To date, distance parameters
involved with assessing risk of a particular storm have been rather arbitrary,
contributing to the necessity in understanding how such parameters influence a
county's exposure status. In assessing the risk of a given storm based on
distance, recent studies have defined the distance from the storm track affected
by a given storm differently. @Czajkowski2011 assessed county-level risk and
exposure based on a three-tierd definition, with primary counties being those
closest to the storm track on either side, secondary counties being adjacent to
primary coutnies, and tertiary counties adjacent to secondary counties. Such a
definition resulted in an exposure defenition based on an average distance
radius of 120 km [75 miles] on either side of the storm track [@Czajkowski2011].
Such a distance is slightly larger than that commonly used by public health
departments (i.e., 100 km) [@Czajkowski2011]. Other studies used distance
buffers of 30 kilometers [@Currie2013] or of 30, 60, and 100 kilometers as
thresholds for identifying distance-based exposure [@Grabich2016] [check the
Grabich paper-- was this distance to any part of a county, or to the center of
the county?; JMF-- I think any part of the county]. Another study used a
distance criterion of 60 kilometers from the storm track, classifying all
counties for which the 60 km buffer fully or partially passed through the
county's boundaries as exposed [@Grabich2015] [again, check to see if this was
to any point in the county or to some center point of the county][JMF-- it is
not abundantly clear in the Grabich 2016 article; based on their graphs it seems
like they considered a county exposed if the definition they used crossed any
county boundary. The Grabich 2015 paper specifies both full and partial counties
being included]. In a study assessing the association between hurricanes and
undesireable birth outcomes, researchers found that results were not sensitive
to the omission of residences 100 km from the storm path, and that results
varied insignificantly from 30-75 km [@Currie2013]. One study used distance to
determine exposure to landfalling US hurricanes by assigning counties along the
storm's tracks as "primary" exposures, counties neighboring primary counties as
"secondary" counties, and counties neighboring secondary counties as "tertiary"
counties; this method correspond to a distance buffer of approximately 75 miles
(120 kilometers) from the storm track for a county to qualify as "exposed" to a
storm [@Czajkowski2011]. The study found that about 30 direct hurricane
fatalities over their study period (1970--2007) occurred outside of this
distance range from the storm center [@Czajkowski2011], suggesting that this
distance choice can cause some counties with dangerous exposures to a storm to
be mis-identified as "unexposed". Tropical cyclones vary dramatically in size:
US tropical cyclones have been observed with radii to maximum winds as small as
20-km and as large as 200-km [@mallin2006; @quiring2011variations].

### 2020-08-17 ehp_revision/response_to_reviewers.Rmd

\begin{shaded}
\textbf{R3 Comment 7:}
Figure 3: The x-axis refers to one of the two wind data sources as "Extended
Best Tracks." Is this the same thing as the wind radii dataset described in the
text? Is so, I suggest clarifying this in the figure label.
\end{shaded}

**Response:**

We have revised the x-axis on the figure to clarify that the comparison is based
on the wind radii dataset described in the text, as requested. The original and
revised versions of this paper are reproduced in this response document as
Figure \@ref(fig:fig3).

```{r fig3, fig.cap="Reproduction of Figure 3 from the original manuscript (left) and revised version in the resubmitted manuscript (right). In the revised version, the x-axis has been labelled to clarify that this axis is showing results based on the wind radii dataset described in the text, in response to Reviewer 3's Comment 7. The revised version also uses a more focused range for the x axis, as requested in EHP's Request 1. Figure caption in the revised manuscript: \\textit{Comparison of two sources of wind exposure estimates: (1) modeled peak sustained surface wind and (2) estimates based on HURDAT2's wind speed radii. Each point represents a storm, with the x-axis giving the percent of counties classified in the same category of peak sustained surface wind (< 34 kt; 34--49.9 kt; 50--63.9 kt; $\\ge$64 kt) by both sources of data. The color of each point gives the number of study counties that were exposed to peak sustained surface wind of at least 34 kt (based on modeled wind). Estimates are shown for study storms since 2004, the earliest year for which post-storm reanalysis wind speed radii are routinely available in HURDAT2, and for which at least one study county had a peak sustained wind of $\\ge$34 kt based on the post-storm wind radii.}", fig.show = "hold", out.width="50%"}
include_graphics("../figures/windcomparison.pdf")
include_graphics("figures/windcomparison.pdf")
```

### 2020-08-17 writing/darlings_methods.tex
Pull in for response from darlings

Ground-based observations of wind speed are problematic for measuring exposure
to tropical cyclones, as instruments often fail at high wind speed, while
reanalysis data---often available at hourly or higher resolution---can lack a
fine enough temporal resolution to capture wind extremes associated with a
tropical cyclone. 
A tropical cyclone's rainfall can can begin a day or more before a
storm and last a day or more after, so this functionality makes it possible to
quantify the cumulative precipitation throughout several days surrounding the
storm's approach.

>>>>

Ground-based observations of wind speed are problematic for measuring exposure
to tropical cyclones, as instruments often fail at high wind speed, while
reanalysis data---often available at hourly or higher resolution---can lack a
fine enough temporal resolution to capture wind extremes associated with a
tropical cyclone.

A tropical cyclone's rainfall can can begin a day or more before a
storm and last a day or more after, so this functionality makes it possible to
quantify the cumulative precipitation throughout several days surrounding the
storm's approach.

\subsection*{Case study}

\textit{The societal impact of a disaster depends both on its geophysical
forcesi, on the population exposed to the hazard, and on the vulnerability of
those living in the geographical areas it
affects~\parencite{chakraborty2005population, anderson2003community,
cutter1996vulnerability}. An estimate of ``physical exposure''---which
...---can help to jointly capture these facets of disaster impacts [ref, maybe
the peduzzi one given below?]. As a case study, we measured physical exposure
based on each metric of exposure and investigated whether conclusions from
these assessments varied substantially.}

We collected data on the number of electricity-dependent Medicare beneficiaries
in each study county from the \ac{US} Department of Health \& Human Service's
emPower Map~2.0~\parencite{empower}. This subpopulation was selected because it
may be particularly susceptible to health impacts from tropical cyclone
exposure, especially through the pathway of storm-associated power outages and
evacuations. We calculated the physical exposure of the electricity-dependent
Medicare population in each county, based on tropical cyclone assessments using
each exposure metric (Table~\ref{tab:exposuremetrics}), following
\citeauthor*{peduzzi2009assessing}~(\citeyear{peduzzi2009assessing}):

\begin{equation}
E_c = F_c * P_c
\end{equation}

\textit{\noindent where~$E_c$ is the average yearly physical exposure among
electricity-dependent Medicare beneficiaries in county~$c$ to tropical cyclone
exposures based on a given metric,~$F_c$ is the estimated yearly expected
frequency of tropical cyclone exposures in county~$c$ based on that metric,
and~$P_c$ is the electricity-dependent Medicare population in
county~$c$, as of July~2017.}
